Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-18 paper.tex
Refine paragraph about foil performance

Bachant and Wosnik observed how maximum performance and 2-D near-wake profiles
are affected by Reynolds number, but here we look deeper. In this study we set
out to measure the effects of scale, i.e. Reynolds number, on the performance of
the turbine, and its more detailed near-wake characteristics. We were looking to
find a threshold scale beyond which a physical model study could reliably
predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.

@@

Turbine performance is strongly dependent on the lift-to-drag ratio $l/d$ acting
on the blades, which is a function of the blades' angles of attack $\alpha$.
These angles of attack are a function of turbine tip speed ratio, induction
(slowing/turning of the free stream flow prior to reaching the turbine), and
turbine rotation or azimuthal angle $\theta$. Looking at static airfoil data, we
see that the static stall angle---the angle just beyond that at which $l/d$ is
maximum, characterized by flow separation near the leading edge---increases with
blade chord Reynolds number $Re_c$. This can be explained as the transition to a
turbulent boundary layer adjacent to the blade delaying separation.

>>>>

Bachant and Wosnik observed how maximum performance and 2-D near-wake profiles
are affected by Reynolds number \cite{Bachant2014}. In this study we set out to
analyze in greater depth the effects of scale, i.e. Reynolds number, on the
performance of the turbine, and its more detailed near-wake characteristics. We
were looking to find a threshold scale beyond which a physical model study could
reliably predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.

@@

Blade performance is generally characterized by the lift-to-drag ratio $l/d$,
which is a function of the foil's angle of attack $\alpha$. The angles of attack
for cross-flow turbine blades are a function of turbine tip speed ratio,
induction (slowing/turning of the free stream flow prior to reaching the
turbine), and turbine rotation or azimuthal angle $\theta$. Looking at static
airfoil data, we see that the static stall angle---the angle just beyond that at
which $l/d$ is maximum---increases with blade chord Reynolds number $Re_c$. This
in general is caused by the blade boundary becoming more turbulent as a fraction
of the chord length, diminishes the negative effects of a laminar separation
bubble occurring near the leading edge. A review of low Reynolds number airfoil
behavior is presented in \cite{Lissaman1983}.
